---
title: 'A Model for Energy-Saving in an IoT Smarthome accounting for End-User Convenience'
author: 'Alistair Francis Bowman Grevis-James'
date: 'November 2019'
institution: 'Royal Melbourne Institute of Technology'
division: 'Computer Sciences'
advisor: 'Dr Hai Dong'
abstract: |
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')` \pagebreak
acknowledgements: |
  I want to thank a few people.
dedication: |
  You can have a dedication here if you wish. 
preface: |
  This is an example of a thesis setup to use the reed thesis document class
  (for LaTeX) and the R bookdown package, in general.
output: 
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_crop: true
    fig_caption: yes
    keep_tex: yes
    highlight: "kate"
bibliography: biblio.bib
csl: computer-science-research-and-development.csl
link-citations: yes
fontsize: 11pt
geometry: margin=0.79in
header-includes:
 \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
 \usepackage{booktabs}
 \usepackage{longtable}
 \usepackage{array}
 \usepackage{multirow}
 \usepackage[table]{xcolor}
 \usepackage{wrapfig}
 \usepackage{float}
 \floatplacement{figure}{H}
 \usepackage{caption, setspace}
 \captionsetup[figure]{font={stretch=1,scriptsize}}
 \captionsetup[figure]{skip=2pt}
 \captionsetup[table]{font={stretch=1,scriptsize}}
 \captionsetup[table]{skip=2pt}
---

```{r message=FALSE, warning=FALSE, include=FALSE}
# all your necessary packages
packages <- c("countrycode",  "cowplot",  "bibtex", "dplyr", "ggExtra", "tidyverse",
              "ggplot2",  "ggridges", "kableExtra", "knitr", "lubridate", "readr",
             "tidyr", "viridis", "reticulate", "ggsci", "scales", "bibtex") 
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.pos = 'H',
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

\pagebreak



#### Algorithm 1
Text
\begin{algorithm}[H]
\DontPrintSemicolon
\SetAlgoLined
\KwResult{Write here the result}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{[array1]}
\Output{Write here the output}
\BlankLine
\While{While condition}{
    instructions\;
    \eIf{condition}{
        instructions1\;
        instructions2\;
    }{
        instructions3\;
    }
}
\caption{Extraction of data from S1 Activities dataset}
\end{algorithm} 





